Ethnicity sensitive author disambiguation using semi-supervised learning

### 2015-10-06 paper/author_disambiguaton.tex
adding missing spaces

Clustering together all signatures from the same block is the least effective
strategy ($0.9409$), but yields anyhow surprisingly decent accuracy, given the
fact it requires almost no computation (\ie, both learning a linkage function
and running agglomerative clustering can be skipped -- only the blocking
function is needed to group signatures). In particular, this result reveals
that author names are not ambiguous in most cases\footnote{This holds for the
data we extracted, but may in the future, with the rise of non-Western
researchers, be an underestimate of the ambiguous cases.} and that only a small
fraction of them requires advanced disambiguation procedures. On the other
hand, both global and block cut thresholding strategies give very good results,
with a slight advantage for block cuts ($0.9814$ versus $0.9830$), as expected.
In case ${\cal S}^\prime_b$ is empty (\eg, because it corresponds to a young
researcher at the beginning of his career), this therefore suggests that either using
a cut-off threshold learned globally from the known data or using SFI would in general give
satisfactory results, only marginally worse than if claimed signatures had been
known.Trying out 3 clustering methods, the results show that \textit {average linkage} was the best one.

>>>>

Clustering together all signatures from the same block is the least effective
strategy ($0.9409$), but yields anyhow surprisingly decent accuracy, given the
fact it requires almost no computation (\ie, both learning a linkage function
and running agglomerative clustering can be skipped -- only the blocking
function is needed to group signatures). In particular, this result reveals
that author names are not ambiguous in most cases\footnote{This holds for the
data we extracted, but may in the future, with the rise of non-Western
researchers, be an underestimate of the ambiguous cases.} and that only a small
fraction of them requires advanced disambiguation procedures. On the other
hand, both global and block cut thresholding strategies give very good results,
with a slight advantage for block cuts ($0.9814$ versus $0.9830$), as expected.
In case ${\cal S}^\prime_b$ is empty (\eg, because it corresponds to a young
researcher at the beginning of his career), this therefore suggests that either using
a cut-off threshold learned globally from the known data or using SFI would in general give
satisfactory results, only marginally worse than if claimed signatures had been
known. Trying out 3 clustering methods, the results show that \textit {average linkage} was the best one.
